%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Engineering Manager} % Job title
  {\href{https://allegro.pl}{Allegro}} % Organization
  {Warsaw, Poland} % Location
  {Oct. 2023–PRESENT} % Date(s)
  {
    \begin {cvitems} % Description(s) of tasks/responsibilities
      \item {Took charge of a team dedicated to the Merchant Payouts area. I prioritized creating an environment that fostered maintenance, innovation, and personal development, ensuring the team had the resources and space needed to excel.}
      \item {Within just a few months, I was appointed as the lead for a new project. In this role, I significantly contributed to project scoping, headcount planning, and coordinated efforts across multiple teams to align on shared objectives. Additionally, I successfully bootstrapped and led one of the newly formed teams.}
    \end {cvitems}
  }

%---------------------------------------------------------
  \multicventry
    {\href{https://www.boclips.com}{Boclips}} % Organization
    {Warsaw, Poland · London, UK} % Location
    {
      \multicventryitem
        {Lead Software Engineer} % Job title
        {Jun. 2020–Sep. 2023} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Streamlined communication between product, design, engineering and the business, ensuring the team received clear, actionable direction.}
            \item {Cultivated a pragmatic engineering culture focused on team well-being and productivity. Successfully organized and led a team offsite to bolster team cohesion and happiness.}
            \item {Stepped in as the interim Product Manager for a year, navigating an unexpected vacancy. Led the team in the successful design, development, and launch of an enhanced version of the company’s B2B app.}
            \item {Embraced people management responsibilities as a lead, conducting regular one-on-one meetings, offering coaching, gathering feedback, and conducting performance reviews. Effectively advocated for and negotiated salary adjustments for team members.}
          \end{cvitems}
        }
      \multicventryitem
        {Software Engineer} % Job title
        {Jun. 2019–Jun. 2020} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Joined Boclips as a Fullstack Engineer on an XP team driven to deliver rich instructional video capabilities to the EdTech industry. We leveraged Kotlin, Spring, MongoDB, Elastisearch, TypeScript and React to build quality REST APIs and user facing web apps.}
            \item {Pioneered an \href{https://www.1edtech.org/standards/lti}{\underline{LTI}} capability on the Boclips platform. The project involved close collaboration with the customer's engineering team, what eventually marked Boclips' successful debut into LTI integrations.}
            \item {As Boclips' first Polish employee, I played a pivotal role in establishing, managing, and staffing the new Warsaw office.}
          \end{cvitems}
        }
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://www.swing.dev}{SwingDev}} % Organization
    {Warsaw, Poland} % Location
    {Jun. 2018–May 2019} % Date(s)
    {
      \begin {cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for scoping, estimation and initial designs for customer projects. Solutions were later delivered in small teams using Node.js tech stack and AWS cloud infrastructure.}
        \item {Involved in hiring new candidates — as one of the interviewers and a person who helped shape and improve the whole process.}
        \item {The company was running regular micro conferences where I had a chance to \href{https://www.youtube.com/watch?v=5zt-jzKHwX8}{\underline{do a talk}} on how you can implement GitOps using Flux and Kubernetes.}
      \end {cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.kainos.com}{Kainos}} % Organization
    {Gdańsk, Poland · London, UK} % Location
    {Feb. 2015–May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of a team kicking off a greenfield project for a new customer and developing the software foundations via Node.js, Express, Java, Spring Boot, JDBI. The project involved close onsite collaboration with the customer, including guidance and mentorship on agile software development practices.}
        % \item {DEFRA: Development of an AngularJS 1.X, Java 7, Spring, Hibernate Microservices web application.}
        \item {Joined several live projects that leveraged agile to deliver software via JVM and JavaScript based technologies in a fullstack manner.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Java Developer} % Job title
    {\href{https://www.soldevelo.com}{SolDevelo}} % Organization
    {Gdynia, Poland} % Location
    {Jun. 2011–Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led one of the teams developing a SCADA system with JBoss Seam, Hibernate and RichFaces. Acted as a technical point of contact for the customer and their development team.}
        \item {Took part in small projects aimed at adopting Android mobile development within the company.}
        \item {Member of a team maintaining and developing an open source microfinancing system Mifos using a Spring-based tech stack.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
